SI

### 2021-03-11 ms/si.Rmd
Fix DT chamber data filtering for 2013 gametophytes

# Subset DT chamber data
chamber_gameto_2013 <- filmy_dt_chamber %>% filter(generation == "gametophyte", year == "2013")
chamber_gameto_2012 <- filmy_dt_chamber %>% 
  filter(
    salt == "MgNO3", 
    year == "2012",
    generation == "gametophyte") %>%
  mutate(group = case_when(
    date_time < "2012-07-17 00:00:00" ~ "a",
    date_time > "2012-07-17 00:00:00" ~ "b"
  ))

>>>>

# Subset DT chamber data
# the datalogger in use changed part way through.
# 10342564 was used in a combined chamber including both sporos and gametos
chamber_gameto_2013_part_1 <- filmy_dt_chamber %>% filter(serial_no == "10342564", year == "2013")
chamber_gameto_2013_part_2 <- filmy_dt_chamber %>% filter(serial_no == "10140659", year == "2013", generation == "gametophyte")

# chamber_gameto_2013 <- filmy_dt_chamber %>% filter(generation == "gametophyte", year == "2013")
chamber_gameto_2013 <- bind_rows(chamber_gameto_2013_part_1, chamber_gameto_2013_part_2)
chamber_gameto_2012 <- filmy_dt_chamber %>% 
  filter(
    salt == "MgNO3", 
    year == "2012",
    generation == "gametophyte") %>%
  mutate(group = case_when(
    date_time < "2012-07-17 00:00:00" ~ "a",
    date_time > "2012-07-17 00:00:00" ~ "b"
  ))
